Synthesizing Quotient Lenses

### 2018-03-07 papers/QuotientLenses/main.tex
Bit of polishing in 3.4

The rest of the inferrence rules for deriving QREs are given in
Figure~\ref{fig:qrerules}.
\subsection{Semantics of QREs}
As we mentioned before, each QRE $c$ enables us to express the whole and kernel
languages $W(c)$ and $K(c)$, an equivalence relation $\eqrel{c}$ on
$\mathcal{L}(W(c))$ that has $\mathcal{L}(K(c))$ as a complete set of
representatives and a canonizing function $\canonizer(c):\mathcal{L}(W(c))
\longrightarrow \mathcal{L}(K(c))$ whose fibres are the same as $\eqrel{c}$.

Figure~\ref{fig:wk} gives the inductive definitions for the whole and
kernel languages $W(c)$ and $K(c)$ of a QRE.
The \kw{squash} and \kw{permutation} combinators give the two interesting
definitions. If $c = \squash{c_1}{c_2}{f}$, then the whole language of $c$ is
$W(c_1) \sep W(c_2)$. This is because the \kw{squash} combinator uses the
function $f : \mathcal{L}(W(c_1)) \longrightarrow \mathcal{L}(W(c_2))$ to maps
any strings from $\mathcal{L}(W(c_1))$ into $\mathcal{L}(W(c_2))$ (leaving the
$c_2$ strings alone), and then canonizes $W(c_2)$ into $K(c_2)$ using
$\canonizer(c_2)$.

>>>>

The rest of the inferrence rules for deriving QREs are given in
Figure~\ref{fig:qrerules}.
\subsection{Semantics of QREs}

\bcp{General typesetting comment: I frequently find the mixture of lens
  expressions and ordinary text hard to read because the fonts used for them
  are rather similar -- I have to look closely to notice that some
  characters have serifs and others don't.  We should not change the regular
  font -- that's mandated by the SIGPLAN style -- but could we make the lens
  font be something a bit more different?}

As we mentioned before, each QRE $c$ enables us to express the whole and kernel
languages $W(c)$ and $K(c)$, an equivalence relation $\eqrel{c}$ on
$\mathcal{L}(W(c))$ that has $\mathcal{L}(K(c))$ as a complete set of
representatives, and a canonizing function $\canonizer(c):\mathcal{L}(W(c))
\longrightarrow \mathcal{L}(K(c))$ whose fibres are the same as $\eqrel{c}$.

Figure~\ref{fig:wk} gives the inductive definitions for the whole and
kernel languages $W(c)$ and $K(c)$ of a QRE.
The \kw{squash} and \kw{permutation} combinators give the two interesting
definitions. If $c = \squash{c_1}{c_2}{f}$, then the whole language of $c$ is
$W(c_1) \sep W(c_2)$. This is because the \kw{squash} combinator uses the
function $f : \mathcal{L}(W(c_1)) \longrightarrow \mathcal{L}(W(c_2))$ to map
any strings from $\mathcal{L}(W(c_1))$ into $\mathcal{L}(W(c_2))$ (leaving the
$c_2$ strings alone), and then canonizes $W(c_2)$ into $K(c_2)$ using
$\canonizer(c_2)$.
